\papertitle

### 2021-03-01 source_separation/paper/paper.tex
Add introduction references

	In this paper, we try a different approach to this problem by experimenting with deep neural architectures. The main idea is to train a model to classify combinations of real instruments and then use it for orchestration. A typical solution for assisted orchestration is a set of triples \emph{instrument-pitch-dynamics} such as \{\texttt{Flute C6 pp, Bassoon C4 mf, Bassoon G4 ff}\}. By training a neural network with real combinations of instrumental notes, it will acquire the ability to identify the presence of each instrument and its associated pitch by building the appropriate latent representation. Thus, when an unknown target sound is given as input, the network will identify which are the best instruments to match the target sound, and it will be able to  deconstruct a complex mixture of timbres into individual instrument notes. This method is motivated by the good results obtained in previous research on musical instruments identification \cite{Benetos07, Kitahara05} and the more recent use of deep neural networks for musical classification \cite{lostanlen16, Bian19}.

	In this paper we perform preliminary experiments with two deep architectures: a convolutional neural network (CNN) with a long short-term memory (LSTM) unit and \emph{ResNet}, a well known residual architecture that already yielded good results for image classification \cite{He15}. We chose to use a CNN because of its success in audio classification \cite{Hershey17} and we decided to include an LSTM unit in it because of its ability to learn long term dependencies in data \cite{Hochreiter97}, which is important given the temporal nature of audio. The codebase for this paper can be found at: \url{}.

@@

	\section{Conclusions}\label{sec:conclusions}
	We think that adding source separation improves orchestration. Unsupervised methods work better because of the data that supervised methods are trained on \cite{Someone:00}

>>>>

	 The codebase for this paper can be found at: \url{}.

@@

	\section{Conclusions}\label{sec:conclusions}
	We think that adding source separation improves orchestration. Unsupervised methods work better because of the data that supervised methods are trained on
